LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-12-10 main.tex
Fix formatting

\begin{table*}
\begin{center}
\begin{tabular}{|c|p{.7\textwidth}|}
\hline
\multicolumn{2}{|p{.95\textwidth}|}
{\lstinline![curvePosition,curveInitialPosition] = seed_curves_from_lambda_max(distance,cgEigenvalue,cgEigenvector,flowDomain,flowResolution)!}\tabularnewline
\hline \hline
\lstinline!distance! & threshold distance for placement of $\lambda_2(x_0)$ maxima\tabularnewline
\hline
\lstinline!cgEigenvalue! & array of Cauchy-Green strain eigenvalues\tabularnewline
\hline
\lstinline!cgEigenvector! & array of Cauchy-Green strain eigenvectors\tabularnewline
\hline
\lstinline!flowDomain! & $2 \times 2$ array to define flow domain\tabularnewline
\hline
\lstinline!flowResolution! & $1 \times 2$ array to define Cauchy-Green strain main grid resolution\tabularnewline
\hline
\lstinline!periodicBc! & optional $1 \times 2$ logical array to specify periodic boundary conditions. Default: \lstinline![false,false]!.\tabularnewline
\hline
\lstinline!nMaxCurves! & optional maximum number of curves (i.e. shrink lines or stretch lines) to generate. Default: \lstinline!numel(cgEigenvalue)!.\tabularnewline
\hline
\lstinline!odeSolverOptions! & optional \lstinline!odeset! structure to specify flow map integration parameters\tabularnewline
\hline
\end{tabular}
\end{center}
\caption{Syntax of the function \lstinline!seed_curves_from_lambda_max!}
\label{t:seed_curves_from_lambda_max syntax}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\begin{tabular}{|c|p{.7\textwidth}|}
\hline
\multicolumn{2}{|p{.95\textwidth}|}
{\lstinline![curvePosition,curveInitialPosition] = seed_curves_from_lambda_max(distance,cgEigenvalue,cgEigenvector,flowDomain, flowResolution)!}\tabularnewline
\hline \hline
\lstinline!distance! & threshold distance for placement of $\lambda_2(x_0)$ maxima\tabularnewline
\hline
\lstinline!cgEigenvalue! & array of Cauchy-Green strain eigenvalues\tabularnewline
\hline
\lstinline!cgEigenvector! & array of Cauchy-Green strain eigenvectors\tabularnewline
\hline
\lstinline!flowDomain! & $2 \times 2$ array to define flow domain\tabularnewline
\hline
\lstinline!flowResolution! & $1 \times 2$ array to define Cauchy-Green strain main grid resolution\tabularnewline
\hline
\lstinline!periodicBc! & optional $1 \times 2$ logical array to specify periodic boundary conditions. Default: \lstinline![false,false]!.\tabularnewline
\hline
\lstinline!nMaxCurves! & optional maximum number of curves (i.e. shrink lines or stretch lines) to generate. Default: \lstinline!numel(cgEigenvalue)!.\tabularnewline
\hline
\lstinline!odeSolverOptions! & optional \lstinline!odeset! structure to specify flow map integration parameters\tabularnewline
\hline
\end{tabular}
\end{center}
\caption{Syntax of the function \lstinline!seed_curves_from_lambda_max!}
\label{t:seed_curves_from_lambda_max syntax}
\end{table*}
